Blocking-resistant communication\\through domain fronting

### 2014-07-31 docs/meek.tex
Swap order of concurrent connections and connection lifetime.
Call the section just "Traffic analysis."
Revise conclusion to traffic analysis.

\section{Resistance to traffic analysis}
\label{sec:trafficanalysis}

One of our goals in developing \meek\ is to force
the censor to use relatively expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ as described is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication like
the packet length distribution and interpacket timing,
or injecting traffic at the risk of causing collateral damage.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

\subsection{Conclusion} So far we do not find any obvious traffic characteristics that can be useful for
distinguishing \meek's traffic. But admittedly there two potential weaknesses: long-lived connections 
with bulk data transfer, and deviated distribution of packet sizes. To fundamentally fix these weaknesses 
we need to transform to the traffic into the normal-looking traffic. The problem is inherently difficult, because we need to know \emph{what} is normal traffic, i.e. what is the model of normal traffic, which is an open problem. However, 
the arm-race game is symmetric; since finding a right model is a difficult task for us, it is also difficult for 
the censor. Therefore, the censor can only find ad-hoc features to block forbidden traffic, which are relatively 
easy to defend against.

>>>>

\section{Traffic analysis}
\label{sec:trafficanalysis}

One of our goals in developing \meek\ is to force
the censor to use relatively expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ as described is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
We hope that the censor will have to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

$$\diamondsuit$$

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it's difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google is likely to be different than Akamai,
and it's hard to characterize what normal use of a CDN is:
they provide access to ordinary web sites,
but also video streams and software updates,
and not all clients are browsers.
The difficulty is symmetric;
if finding the right model is difficult task for us,
it is also difficult for the censor.
We have seen that censors prefer to use easy classifiers when they exist.
By removing the easy ways, we increase the cost to the censor.
